Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-04-05 paper-correlations.tex
Try to explain what periodic/non-periodic boundary conditions are

Correlation functions can be computed using closed walls (CW) and periodic
boundary conditions. \textbf{TODO: Describe them}.

@@

\appendix
\section{Algorithm of computation of lineal-phase function}
\label{linpathalg}
The algorithm below calculates $L_2^{(phase)}$ correlation function for
one-dimensional array $a$. The result is an array of $L_2$ values for
correlation lengths from $0$ to $maxlen-1$. If $periodic$ is true (resp. false)
then periodic (resp. CW) boundary conditions are used. The entry point of the
algorithm is the function L2. The efficiency of the proposed algorithm is $O(n)$
where $n$ is the length of the array.

>>>>

Correlation functions can be computed using periodic and zero-padding boundary
conditions. With periodic boundary conditions a correlation function is
calculated as if the input array were periodically extended to infinity,
i.e. $A_k = A_{k+N_k}$ where $N_k$ is the k-th array dimension. With
zero-padding the input is extended with zeros, i.e. $A_k = 0$ when
$0 < k < N_k$.

@@

\appendix
\section{Algorithm of computation of lineal-phase function}
\label{linpathalg}
The algorithm below calculates $L_2^{(phase)}$ correlation function for
one-dimensional array $a$. The result is an array of $L_2$ values for
correlation lengths from $0$ to $maxlen-1$. If $periodic$ is true (resp. false)
then periodic (resp. zero padding) boundary conditions are used. The entry point of the
algorithm is the function L2. The efficiency of the proposed algorithm is $O(n)$
where $n$ is the length of the array.
